\textit{Supplementary Material} \\ Predicting Solid State Material Platforms for Quantum Technologies

### 2022-03-05 supplementary.tex

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[superscriptaddress,unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

@@

\usepackage{sansmath}
\tikzset{>=stealth,
OptimumStyle/.style={align=center,anchor=east,rotate=90,font=\scriptsize}
}
\pgfplotsset{%samples=101,
axis lines = left,
every axis plot/.append style={line width=2pt},
}
% Include font for the identity operator
\usepackage{dsfont}
\usepackage[binary-units=true]{siunitx}
\usepackage{makecell}
\usepackage{longtable}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
\usepackage{siunitx}
\usepackage{color}
\sisetup{separate-uncertainty}

\usepackage{forest}
\forestset{
    .style={
        for tree={
            base=bottom,
            child anchor=north,
            align=center,
            s sep+=1cm,
    straight edge/.style={
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -- (.child anchor);}
    },
    if n children={0}
        {tier=word, draw, thick, rectangle}
        {draw, diamond, thick, aspect=2},
    if n=1{%
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {Y};}
        }{
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {N};}
        }
        }
    }
}
\tikzset{
  green arrow/.style={
    midway,green,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
    allow upside down
  },
  yellow arrow/.style={
    midway,yellow,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
    allow upside down
  },
  black arrow/.style 2 args={-stealth, shorten >=#1, shorten <=#2},
  black arrow/.default={1mm}{1mm},
  tree box/.style={draw, rounded corners, inner sep=1em},
  node box/.style={white, draw=white, text=black, rectangle, rounded corners},
}

@@

The implementation of the machine learning methods was achieved through the machine learning library Scikit-learn \cite{Pedregosa2012}. Adjusting many of the hyperparameters in Scikit-learn resulted in severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees. Therefore, most parameters are the default values defined by Scikit-learn. The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown. In our work we adjusted 
%between 
the depth of the trees to vary from $1$ to $8$. For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and used either $200$ or $400$ iterations to reach convergence.

@@

\begin{table}[t]
\centering
\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:01-pca}.}
\label{tab:01-pc}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
  \hline
  LOG & $171$ & $0.98(0.012)$ & $0.98(0.011)$ & $0.99(0.007)$ & $0.99(0.007)$ \\
  DT & $37$   & $0.77(0.034)$ & $0.84(0.034)$ & $0.85(0.044)$ & $0.84(0.022)$ \\
  RF & $53$   & $0.87(0.027)$ & $0.88(0.022)$ & $0.98(0.010)$ & $0.93(0.014)$ \\
  GB & $107$  & $0.92(0.016)$ & $0.92(0.015)$ & $0.98(0.010)$ & $0.95(0.009)$ \\
  \hline
\end{tabular}
}
\end{table}

In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components. The optimal number  is visualized as dotted lines in Fig.~\ref{fig:01-pca}. The relevant hyperparameters for logistic regression were the maximum iterations. The number of iterations was set at $400$, and the regularization term was given by an optimal of $0.46$. For random forests and decision trees, we find the maximum depth of $7$. Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$. We find the best performing method to be logistic regression, but this method depends on a large number of principal components.

@@

\begin{table}[t]
\centering
\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:02-pca}.}
\label{tab:02-pc}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
  \hline
  LOG & $175$ & $0.98(0.008)$ & $0.99(0.004)$ & $0.99(0.004)$ & $0.99(0.003)$ \\
  DT & $25$   & $0.69(0.034)$ & $0.86(0.015)$ & $0.93(0.021)$ & $0.90(0.008)$ \\
  RF & $25$   & $0.70(0.028)$ & $0.86(0.011)$ & $1.00(0.003)$ & $0.93(0.006)$ \\
  GB & $93$   & $0.85(0.025)$ & $0.93(0.011)$ & $0.99(0.004)$ & $0.96(0.007)$ \\
  \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[t]
\centering
\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Fig.~\ref{fig:03-pca}.}
\label{tab:03-pca}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test & Mean precision & Mean recall  & mean F1\\
  \hline
  LOG & $61$  & $0.99(0.011)$ & $0.97(0.032)$ & $0.99(0.016)$ & $0.98(0.018)$ \\
  DT & $9$    & $0.96(0.019)$ & $0.95(0.040)$ & $0.95(0.033)$ & $0.95(0.026)$ \\
  RF & $27$   & $0.98(0.020)$ & $0.97(0.033)$ & $0.97(0.031)$ & $0.97(0.026)$ \\
  GB & $13$   & $0.97(0.016)$ & $0.96(0.036)$ & $0.97(0.029)$ & $0.96(0.022)$ \\
  \hline
\end{tabular}
}
\end{table}

@@

%histograms 
\begin{figure}[t]
\label{fig:histograms_supp}
\begin{subfigure}[t]{1\textwidth}
    \input{figures/histograms/new/legend.tex}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ElementProperty_MagpieData range CovalentRadius_count_075.tex}}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MaximumPackingEfficiency_max packing efficiency_count_075.tex}}
    \subcaption{}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.tex}}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MP_Eg_normalized_databackgrund_075.tex}}
    \subcaption{}
\end{subfigure}
\caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$. Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function. Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set. 
%The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. 
The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
\end{figure}

>>>>

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[floatfix, superscriptaddress,unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

@@

\usepackage{sansmath}
\tikzset{>=stealth,
OptimumStyle/.style={align=center,anchor=east,rotate=90,font=\scriptsize}
}
\pgfplotsset{%samples=101,
axis lines = left,
every axis plot/.append style={line width=2pt},
}
% Include font for the identity operator
\usepackage{dsfont}
\usepackage[binary-units=true]{siunitx}
\usepackage{makecell}
\usepackage{longtable}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
\usepackage{siunitx}
\usepackage{color}
\sisetup{separate-uncertainty}
\UseRawInputEncoding
\usepackage{forest}
\forestset{
    .style={
        for tree={
            base=bottom,
            child anchor=north,
            align=center,
            s sep+=1cm,
    straight edge/.style={
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -- (.child anchor);}
    },
    if n children={0}
        {tier=word, draw, thick, rectangle}
        {draw, diamond, thick, aspect=2},
    if n=1{%
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {Y};}
        }{
        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {N};}
        }
        }
    }
}
\tikzset{
  green arrow/.style={
    midway,green,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
    allow upside down
  },
  yellow arrow/.style={
    midway,yellow,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
    allow upside down
  },
  black arrow/.style 2 args={-stealth, shorten >=#1, shorten <=#2},
  black arrow/.default={1mm}{1mm},
  tree box/.style={draw, rounded corners, inner sep=1em},
  node box/.style={white, draw=white, text=black, rectangle, rounded corners},
}

@@

The implementation of the machine learning methods was achieved through the machine learning library Scikit-learn \cite{Pedregosa2012}. Adjusting many of the hyperparameters in Scikit-learn resulted in severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees. Therefore, most parameters are the default values defined by Scikit-learn. The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum depth for the trees grown. In our work we adjusted 
%between 
the depth of the trees to vary from $1$ to $8$. For logistic regression, we chose to adjust the regularization strength with seven logarithmic values ranging from $10^{-3}$ to $10^{5}$, and used either $200$ or $400$ iterations to reach convergence.

@@

\begin{table}[t]
\centering
\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:01-pca}.}
\label{tab:01-pc}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{2.0cm} M{1.5cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test & Mean precision & Mean recall & mean F1\\
  \hline
  LOG & $171$ & $0.98(0.012)$ & $0.98(0.011)$ & $0.99(0.007)$ & $0.99(0.007)$ \\
  DT & $37$   & $0.77(0.034)$ & $0.84(0.034)$ & $0.85(0.044)$ & $0.84(0.022)$ \\
  RF & $53$   & $0.87(0.027)$ & $0.88(0.022)$ & $0.98(0.010)$ & $0.93(0.014)$ \\
  GB & $107$  & $0.92(0.016)$ & $0.92(0.015)$ & $0.98(0.010)$ & $0.95(0.009)$ \\
  \hline
\end{tabular}
}
\end{table}

In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components. The optimal number is visualized as dotted lines in Fig.~\ref{fig:01-pca}. The relevant hyperparameters for logistic regression were the maximum iterations. The number of iterations was set at $400$, and the regularization term was found optimal at $0.46$. For random forests and decision trees, we find the maximum depth to be $7$. Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$. We find the best performing method to be logistic regression, but this method depends on a large number of principal components.

@@

\begin{table}[t]
\centering
\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:02-pca}.}
\label{tab:02-pc}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{2.0cm} M{1.5cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
  \hline
  LOG & $175$ & $0.98(0.008)$ & $0.99(0.004)$ & $0.99(0.004)$ & $0.99(0.003)$ \\
  DT & $25$   & $0.69(0.034)$ & $0.86(0.015)$ & $0.93(0.021)$ & $0.90(0.008)$ \\
  RF & $25$   & $0.70(0.028)$ & $0.86(0.011)$ & $1.00(0.003)$ & $0.93(0.006)$ \\
  GB & $93$   & $0.85(0.025)$ & $0.93(0.011)$ & $0.99(0.004)$ & $0.96(0.007)$ \\
  \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[t]
\centering
\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Fig.~\ref{fig:03-pca}.}
\label{tab:03-pca}
\noindent\makebox[\textwidth]{
\begin{tabular}{M{2.0cm} M{1.5cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
  \hline
  \hline
   Method & PC & Mean test & Mean precision & Mean recall  & mean F1\\
  \hline
  LOG & $61$  & $0.99(0.011)$ & $0.97(0.032)$ & $0.99(0.016)$ & $0.98(0.018)$ \\
  DT & $9$    & $0.96(0.019)$ & $0.95(0.040)$ & $0.95(0.033)$ & $0.95(0.026)$ \\
  RF & $27$   & $0.98(0.020)$ & $0.97(0.033)$ & $0.97(0.031)$ & $0.97(0.026)$ \\
  GB & $13$   & $0.97(0.016)$ & $0.96(0.036)$ & $0.97(0.029)$ & $0.96(0.022)$ \\
  \hline
\end{tabular}
}
\end{table}

@@

%histograms 
\begin{figure}[!t]
\begin{subfigure}[t]{1\textwidth}
    \input{figures/histograms/new/legend.tex}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ElementProperty_MagpieData range CovalentRadius_count_075.tex}}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MaximumPackingEfficiency_max packing efficiency_count_075.tex}}
    \subcaption{}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.tex}}
    \subcaption{}
\end{subfigure}
\begin{subfigure}[b]{0.45\textwidth}
    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MP_Eg_normalized_databackgrund_075.tex}}
    \subcaption{}
\end{subfigure}

\caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$. Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function. Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set. 
%The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. 
The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
\label{fig:histograms_supp}
\end{figure}
